### 2018-10-05 figures/A1_iris.Rmd
fill-out skeleton

```{r 01_iris, echo=FALSE, warning=FALSE, fig.width = 5.5, fig.height = 3}
ggplot() + 
  geom_point(data = iris, aes(x = Sepal.Length, y = Sepal.Width))
```

>>>>

```{r A1_iris, echo=FALSE, warning=FALSE, fig.width = 5.5, fig.height = 3}
ggplot() + 
  geom_point(data = iris, aes(x = Sepal.Length, y = Petal.Length))
```

### 2018-10-05 tables/01_iris_table.Rmd
fill-out skeleton

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
---

@@

```{r load_data, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
# setwd("figures")
source("../scripts/01.5_loaddata.R")
```

```{r A1_iris, echo=FALSE, warning=FALSE, fig.width = 5.5, fig.height = 3}
ggplot() + 
  geom_point(data = iris, aes(x = Sepal.Length, y = Petal.Length))
```

>>>>

---
output:
  pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

@@

```{r load_data, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
source("../scripts/01.5_loaddata.R")
```

```{r iris_table, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
knitr::kable(head(iris), caption = "Iris table")
```
